---
title: "Project"
---

```{r -read in packages}
#| echo: false
#| warning: false
#| message: false

#loading packages
library(tidyverse)
library(janitor)
library(here)
library(flextable)
library(readxl)
library(png) 
library(grid) 
#loading data
my_data <- read.csv(here("my_data.csv"))
```

```{r}
#| warning: false
#| message: false

#| fig-cap:The circular bar graph titled "Spending Spiral: Money Spent on Campus by Day" visualizes the amount of money spent on campus, broken down by each day of the week. Utilizing a polar coordinate transformation of a standard bar chart, the graph presents daily spending amounts as radial segments, giving the impression of a pie or spiral chart. Each day's spending is represented with a distinct color gradient from the Viridis palette, providing clear visual separation and accessibility-friendly contrast. Notably, Thursday stands out with a dramatically larger segment than the others, clearly indicating an unusually high expenditure on that day. This spike is the result of an outlier incident when the user's tire popped, requiring an unplanned repair that cost over $30. In contrast, the segments for the other days are relatively uniform and small, reflecting more typical, lower daily spending. The use of a void theme keeps the visual clean and focused solely on the data, and the circular format adds an engaging and unconventional aesthetic while still conveying the proportional nature of the spending data.

# creating circle graph
ggplot(my_data, aes(x = day, y = spent, fill = day)) + #using my original data not summary data
  geom_bar(stat = "identity", position = 
             "dodge", show.legend = TRUE) +
  #creating a base bar graph
  coord_polar() + #changing the bar graph to circle 
  theme_void() + #theme
  scale_fill_viridis_d() +
  labs(title = "Spending Spiral: Money Spent on campus by Day") +
  # title 
  theme(title = element_text(size =14))# changing the size of title
```



![This project poster was from conservation planning class. This poster effectively communicates a detailed and interdisciplinary conservation strategy through a combination of scientific rigor, stakeholder engagement, and clear visual storytelling. It showcases a real-world application of environmental science and policy with both ecological and community-based lenses. The inclusion of structured planning tools like MCDA and consequence tables underscores a strong methodological foundation for decision-making.](ES 137.S2024.AlaskanGiantKelpForests.png)