---
title: "Project"
---

```{r -read in packages}
#| echo: false
#| warning: false
#| message: false

#loading packages
library(tidyverse)
library(janitor)
library(here)
library(flextable)
library(readxl)
library(png) 
library(grid) 
#loading data
my_data <- read.csv(here("my_data.csv"))
```

```{r}
#| warning: false
#| message: false

# creating circle graph
ggplot(my_data, aes(x = day, y = spent, fill = day)) + #using my original data not summary data
  geom_bar(stat = "identity", position = 
             "dodge", show.legend = TRUE) +
  #creating a base bar graph
  coord_polar() + #changing the bar graph to circle 
  theme_void() + #theme
  scale_fill_viridis_d() +
  labs(title = "Spending Spiral: Money Spent on campus by Day") +
  # title 
  theme(title = element_text(size =14))# changing the size of title
```

In my circular bar graph titled "Spending Spiral: Money Spent on Campus by Day," I visualized how much money I spent on campus across different days of the week. I used a polar coordinate transformation on a regular bar chart to create a spiral-like display, where each day is represented as a distinct radial segment. I applied a Viridis color scale to make each day easy to distinguish, and I kept the overall design clean with a minimal theme so the focus stays on the data. One segment, Thursday, is noticeably larger than the others, and that’s because of an outlier: my tire popped that day, and I ended up spending over $30 to get it fixed. That unexpected cost makes Thursday look dramatically higher than the rest. Most of the other days show much smaller and more consistent spending, giving a clearer picture of my usual on-campus expenses.




![This project poster was from conservation planning class. This poster effectively communicates a detailed and interdisciplinary conservation strategy through a combination of scientific rigor, stakeholder engagement, and clear visual storytelling. It showcases a real-world application of environmental science and policy with both ecological and community-based lenses. The inclusion of structured planning tools like MCDA and consequence tables underscores a strong methodological foundation for decision-making.](ES 137.S2024.AlaskanGiantKelpForests.png)